Exploratory data analysis

### 2022-07-01 slides/data_checking.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      dev = "svglite",
                      message = FALSE,
                      warning = FALSE,
                      fig.asp = 3/4)

@@

@@

```{r}
r_facts %>% 
  mutate(ep_is_same = recode(ep_is_same,
                                         `0` = "ep diff",
                                         `1` = "ep same"),
                     sem_is_same = recode(sem_is_same,
                                          `0` = "sem diff",
                                          `1` = "sem same")) %>% 
  group_by(subj_num, j_score, ep_is_same, sem_is_same) %>% 
  summarize(mean_acc = mean(acc_recall)) %>% 
  ggplot(aes(x = interaction(ep_is_same, sem_is_same), y = mean_acc,
             group = subj_num,
             color = j_score)) +
  geom_line() +
  geom_point() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_color_viridis_c() +
  labs(x = "Chunk type", y = "Percent facts correctly recalled", color = "Expertise score") +
  theme_bw()
```

@@

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  mutate(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy with confidence")
```

@@

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  mutate(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy with confidence")
```

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      dev = "svglite",
                      message = FALSE,
                      warning = FALSE,
                      fig.asp = 7/10)

@@

???

Check whether category assignment is related to expertise

@@

Now filtered to include only not-previously-known facts

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(ep_is_same = recode(ep_is_same,
                                         `0` = "ep diff",
                                         `1` = "ep same"),
                     sem_is_same = recode(sem_is_same,
                                          `0` = "sem diff",
                                          `1` = "sem same")) %>% 
  group_by(subj_num, j_score, ep_is_same, sem_is_same) %>% 
  summarize(mean_acc = mean(acc_recall)) %>% 
  ggplot(aes(x = interaction(ep_is_same, sem_is_same), y = mean_acc,
             group = subj_num,
             color = j_score)) +
  geom_line() +
  geom_point() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_color_viridis_c() +
  labs(x = "Chunk type", y = "Percent facts correctly recalled", color = "Expertise score") +
  theme_bw()
```

???

Fix this graph to filter for didn't already know

Look at RT measures as a function of chunk type! Difference between start and finish normalized by answer length?

@@

```{r}
this_cor <- r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %$% 
  cor(j_score, acc) %>% 
  round(2)
```

Pearson correlation shown: `r this_cor`

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
```

```{r}
this_cor <- r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %$% 
  cor(j_score, acc) %>% 
  round(2)
```

Pearson correlation shown: `r this_cor`

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
```

@@

```{r}
this_cor <- r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %$% 
  cor(j_score, acc) %>% 
  round(2)
```

Pearson correlation shown: `r this_cor`

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
```

```{r}
this_cor <- r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %$% 
  cor(j_score, acc) %>% 
  round(2)
```

Pearson correlation shown: `r this_cor`

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
```

@@

???

Sanity check these against the apparent effect where high experts seem to be doing worse on photo memory?

@@

???

Sanity check this one as well

@@

???

Include interest in the other models
